---
title: "A Homework of Biblical Proportions"
author: "Chung-Ting Yang"
output: html_document
---

In this HW, we will analyze the text of the bible. The ascii version resides in the file "ascii_bible.txt" on Camino. Use an editor to familiarize yourself with the structure of the file. Then perform the following operations, listed below as questions for you to answer. 

## Q1: Read in the file using any R function you like and store each verse in a text array. After which print the top 20 verses. (Remove the top two lines which contain the title.)

```{r}

rm(list=ls())
library(stringr)
answer1 = "ascii_bible.txt"
answer1 = readChar(answer1, file.info(answer1)$size)
answer1 = unlist(strsplit(answer1, "\n\n"))
answer1 = gsub("\n", "", answer1)
answer1 = str_replace(gsub("\\s+", " ", str_trim(answer1)), "B", "b")
answer1 = answer1[3:(length(answer1))]
answer1[1:20]

```

## Q2: How many verses are there in total? 

```{r}

answer2 = length(answer1) 
answer2

```

## Q3: Each verse has the number "CCC:VVV" where CCC is the chapter number and VVV is the verse number. How many chapters are there? 

#### 150
```{r}
verse = list()
Number  = c() 

for(i in 1:length(answer1)){
 verse = c(verse,strsplit(answer1[i], " "))
 Number = c(Number, verse[[i]][1])
}

answer3 = unique(str_sub(Number,1,3))
answer3



```


## Q4: Extract an array for the verse numbers, and also one for the verse text.

```{r}

answer4 = strsplit(answer1, " ")

number_array = c()
text_array =  c()  

for (x in 1:length(answer4)){
  text_array = c(text_array, paste(answer4[[x]][-1], sep = " ",collapse=" "))
  number_array = c(number_array, answer4[[x]][1])
}

head(number_array)
head(text_array)


```

## Q5: Lower case all text.

```{r}

answer5 = tolower(text_array)
head(answer5)

```

## Q6: Convert the text of all verses into a Corpus using the **tm** package. 

```{r}

library(tm)
answer6 =  VectorSource(answer5)
answer6 = Corpus(answer6)

head(answer6$content)

```

## Q7: Remove all punctuation. Use a corpus function for this. How many unique words are there in the bible? 

```{r}

Pun = tm_map(answer6, removePunctuation)
word = (c(strsplit(Pun$content, " ")))

answer7 = c()
for (x in 1:length(word)){
  answer7 = c(answer7, word[[x]])
}

answer7 = length(unique(answer7))
answer7


```

## Q8: Remove all stopwords. Now how many unique terms are there? 

```{r}

stopword = tm_map(Pun, removeWords, stopwords("en"))
word2 = (c(strsplit(stopword$content, " ")))

answer8 = c()
for (x in 1:length(word2)){
  answer8 = c(answer8, word2[[x]])
}

answer8 = length(unique(answer8))
answer8

```

## Q9: Now stem the text, to remove multiplicity of similar words of the same root. 

```{r}

answer9 = tm_map(stopword, stemDocument)
head(answer9$content)

```

## Q10: How many distinct words are there in the bible, after stemming?

```{r}

word3 = (c(strsplit(answer9$content, " ")))

answer10 = c()
for (x in 1:length(word3)){
  answer10 = c(answer10, word3[[x]])
}

answer10 = length(unique(answer10))
answer10


```

## Q11: Convert the TDM into a matrix and find the 50 most common words in the bible. 

```{r}

answer11 = TermDocumentMatrix(answer9)
answer11 = as.matrix(answer11)

sort(rowSums(answer11), decreasing = TRUE)[1:50]


```

## Q12: Make a wordcloud of the top 100 words in the bible. 

```{r}
library(wordcloud)

Top100 = sort(rowSums(answer11), decreasing = TRUE)[1:100]

answer12 = data.frame(Top100, term = names(Top100),num = Top100)
wordcloud(answer12$term, answer12$num, max.words = 100, colors = "pink2")



```

## Q13: Mood score the original text of the bible (before stemming)

```{r}

library(ngram)
library(NLP)
library(syuzhet)

answer13 = get_tokens(stopword$content)
answer13 = get_sentiment(answer13)
sum(answer13)

```

## Q14: Summarize the bible into less than 500 verses. (Or some fraction of the total number of verses, it's your choice.) Be super careful here as this may take a long time unless you are clever about it, or find some elegant way to speed things up!

```{r}

library(lsa)

TF_IDF = as.matrix(weightTfIdf(TermDocumentMatrix(stopword)))
Mean = rowMeans(TF_IDF)

Score = c()
for(x in 1:ncol(TF_IDF)){
 Score = c(Score, cosine(Mean, TF_IDF[,x]))
}

index = which(Score %in% sort(Score, decreasing = TRUE)[1:500])

answer14 = answer9$content[index]
answer14


```

## Q15: Find the main 3 topics in the bible, and the top 25 words in each topic. Can you find an interpretation of each topic?

```{r}

library(text2vec)

tokens = answer9$content %>% tolower %>% word_tokenizer
it = itoken(tokens, ids = c(1:length(answer9$content)), progressbar = FALSE)
v = create_vocabulary(it) %>% prune_vocabulary(term_count_min = 10, doc_proportion_max = 0.2)
vectorizer = vocab_vectorizer(v)
dtm = create_dtm(it, vectorizer, type = "dgTMatrix")

lda_model = LDA$new(n_topics = 3, doc_topic_prior = 0.1, topic_word_prior = 0.01)
doc_topic_distr = lda_model$fit_transform(x = dtm, n_iter = 1000, convergence_tol = 0.001, n_check_convergence = 25, progressbar = FALSE)

lda_model$get_top_words(n = 25, topic_number = c(1L, 2L, 3L), lambda = 1)


```
